Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-04-02 parts/sa.tex
section 3

The reachability of a process $a_i$ of a sort $a$ from another process $a_j$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  The reachability of a process $a_j$ prof a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.
\end{definition}
\noindent
We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
The set of all objective sequences is denoted by $\OS$.

A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
We also extend the notion of override of a context by a set of processes (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
%$\supp(\delta) \subseteq \ctx$. 
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

@@

Finally, bounce sequences on a sort (\pref{def:bs}) are sequences of actions in which the bounce of each action equals the hitter of the following action.
Bounce sequences are used to find sequences of actions that locally solve a given objective.
%solve an objective locally, by finding the sequences of actions that allow to reach a process.
Bounce sequences can be abstracted into the sets of hitters of every action that are different from the considered sort (\pref{def:aBS}).
This abstraction allows to propagate an objective into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  Obviously, $\BS(\obj{a_i}{a_i}) = \{\emptyseq\}$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
\label{def:aBS}
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
%if such a scenario exists in all states $s \subseteq \ctx$.

\begin{comment}
\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}
\end{comment}

\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset$.
\end{theorem}

@@

The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
The set of all processes involved in such a graph $(\V, \E)$ is given in \pref{def:allprocs}.
For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
by computing $\gCont_\ctx(\PHsort(P), P)$.
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  \end{align*}
\end{definition}
%
\begin{comment}
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}
\end{comment}
%
%\subsection{Abstract structure}
%
%
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

@@

\towrite{expliquer le graphe de causalité}

\begin{definition}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}

@@

In the following, we denote:
%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.

\begin{comment}
\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}
\end{comment}

\towrite{Expliquer}

\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said coherent if and only if:
  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
%  A set of processes $ps \in \Bv \cap \powerset(\PHproc)$ is said coherent if and only if
%  it has no process successor $a_j \in \Bv \cap \PHproc$ so that there exists $a_i \in ps$, $a_i \neq a_k$.
\end{definition}

\towrite{Expliquer}

>>>>

The reachability of a process $a_i$ of a sort $a$ from another process $a_j$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
\begin{definition}[Objective ($\Obj$)]
\label{def:obj}
  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
  and $P$ is \emph{trivial} if $a_i = a_j$.
\end{definition}
\noindent
We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
The set of all objective sequences is denoted by $\OS$.

A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
We also extend the override operator to a context and a set of processes (\pref{def:ctxcap}).
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
%
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
%$\supp(\delta) \subseteq \ctx$. 
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.

@@

Finally, bounce sequences on a sort $a$ (\pref{def:bs}) are sequences of actions hitting $a$ in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find sequences of actions that locally solve a given objective.
%solve an objective locally, by finding the sequences of actions that allow to reach a process.
A bounce sequence can be abstracted into its sets of hitters that are not in sort $a$.
%of every action that are different from the considered sort (\pref{def:aBS}).
This abstraction allows to propagate an objective into objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
\end{definition}
%
\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
\label{def:aBS}
  \[
    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
\end{definition}

@@

We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
\pref{th:uconcr-ctx} will be used to over-approximate the initial context $\ctx$.
%if such a scenario exists in all states $s \subseteq \ctx$.
%
\begin{comment}
\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
\label{def:concr}
\towrite{Simplifier ? Supprimer la def formelle ?}
  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
  \begin{align*}
    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
    \\ &
      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
    \\ &
      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
    \}
    \enspace,
  \end{align*}
  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
\end{definition}
%
\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
\label{def:concr-set}
  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
\end{definition}
\end{comment}
%
\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \uconcr(\w) = 
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{theorem}
\label{th:uconcr-ctx}
  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
\end{theorem}

@@

For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{comment}
\begin{definition}
\label{def:allprocs}
  \begin{align*}
  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  \end{align*}
  \begin{align*}
  \allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}
  \end{align*}
\end{definition}
\end{comment}
%
\begin{comment}
\begin{definition} \todo{À revoir avec la nouvelle sémantique}
\label{def:allprocs}
  \begin{align*}
  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
  \end{align*}
\end{definition}
\end{comment}
%
%\subsection{Abstract structure}
%
%
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) = 
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

@@

The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives in other sorts.
Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
in which edges link any required processes $a_i \in \Proc$ to all corresponding objectives $P \in \Obj$,
and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
such sets $ps$ then stand for new required processes.
In the case where a process $a_i$ belongs to a cooperative sort, it is directly linked to the set of the processes $\csState(a_i)$ (\pref{def:csState}) that it represents.
If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
Finally, as the active process of every sort may evolve, the graph $\cwB$ is iteratively saturated by every process it contains,
by overriding its initial context $\ctx$ with $\allprocs(\V, \E)$, defined by:
%in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
%The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
%This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
%We denote $\allprocs(\V, \E)$ the set of all processes involved in such a graph $(\V, \E)$, defined by: %in \pref{def:allprocs}.
$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$

%The final graph of local causality is computed by a fixed point 
%is defined as a fixed point

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
  \begin{align}
    \w &\subset \cwV \label{eq:Vw} \\
%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
  \end{align}
\end{definition}

@@

In the following, we denote:
%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
%
\begin{comment}
\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
  \end{align*}
\end{definition}

\begin{definition}[Coherent solution]
\label{def:coherent}
  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
\end{definition}
\end{comment}
%
%\towrite{Expliquer}
%We define in \pref{def:coherent} the notion of coherent edge in the graph of local causality.
In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is coherent if none of the successor processes of $ps$ conflict with the processes of $ps$ (\pref{def:coherent}).
Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
which is derived immediately from the graph of local causality.
A proof of this theorem is given in Annex~\ref{suppl:demoapproxinf}.
\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said coherent if and only if:
  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
\end{definition}

\begin{theorem}[Under-Approximation]
\label{th:approxinf}
  If the graph $\cwB$ contains no cycle,
  all objectives have at least one solution
  and all edges are coherent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}
